---
title: "Lab Assignment 2"
author: "Si Chen"
date: "11/8/2018"
output:
  pdf_document: default
  html_document: default
---

```{r}
redwine <- read.table("redwine.txt", header = TRUE)
```

#Problem 1
```{r}
mean(redwine$RS, na.rm = TRUE)
mean(redwine$SD, na.rm = TRUE)
```

The average of RS is 2.537952.
The average of SD is 46.29836.

#Problem 2
```{r}
SD.obs <- na.omit(redwine$SD)
FS.obs <- redwine$FS[!is.na(redwine$SD)]
fit1 = lm(SD.obs ~ FS.obs)
coefficients(fit1)
```

#Problem 3
```{r}
FS.impute <- redwine$FS[is.na(redwine$SD)]
SD.impute <- coefficients(fit1)[2] * FS.impute + coefficients(fit1)[1]
redwine$SD[is.na(redwine$SD)] = SD.impute
mean(redwine$SD)
```

The average of SD after imputation is 46.30182.

#Problem 4
```{r}
avg.imp <- function (a, avg){
        missing <- is.na(a)
        imputed <- a
        imputed[missing] <- avg
        return (imputed)
   }
RS_avg = mean(na.omit(redwine$RS))
RS.avgimp = avg.imp(redwine$RS,RS_avg)
mean(RS.avgimp)
```

The average of RS after imputation is 2.537952.

#Problem 5
```{r}
redwine$RS <- RS.avgimp
fit = lm(QA ~ ., data = redwine)
coefficients(fit)
```

#Problem 6
```{r}
summary(fit)
```

PH has the largest p-value, therefore is the least likely to be related to QA.

#Problem 7
```{r}
CVInd <- function(n,K) {  
   m<-floor(n/K)  
   r<-n-m*K  
   I<-sample(n,n)  
   Ind<-list()  
   length(Ind)<-K
   for (k in 1:K) {
      if (k <= r) kpart <- ((m+1)*(k-1)+1):((m+1)*k)  
         else kpart<-((m+1)*r+m*(k-r-1)+1):((m+1)*r+m*(k-r))
      Ind[[k]] <- I[kpart]  #indices for kth part of data
   }
   Ind
}

Nrep <- 20 
K <- 5  
n = nrow(redwine)
y<-redwine$QA
SSE <- c()
for (j in 1:Nrep) {
  Ind<-CVInd(n,K)
  yhat <- y
  for (k in 1:K) {
     out <- lm(QA~.,data = redwine[-Ind[[k]],])
     yhat[Ind[[k]]] <- as.numeric(predict(out,redwine[Ind[[k]],]))
  } 
  SSE = c(SSE,sum((y-yhat)^2))
} 
SSE
mean(SSE)
```

#Probelem 8
```{r}
PH.mean = mean(redwine$PH)
PH.sd = sd(redwine$PH)
PH.mean
PH.sd
PH.lb = PH.mean - 3 * PH.sd
PH.ub = PH.mean + 3 * PH.sd
redwine2 <- subset(redwine, redwine$PH < PH.ub & redwine$PH > PH.lb)
dim(redwine2)
dim(redwine)
dim(redwine)[1] - dim(redwine2)[1]
```

The average of PH is 3.306202.
The standard deviation of PH is 0.3924948.
redwine2 has 1580 rows. 19 observations are removed.

#Problem 9
```{r}
fit_new = lm(QA ~ ., data = redwine2)
summary(fit_new)
```

The new model is better because the R-squared increases.
VA, CH, SD, SU, AL are attributes having the 5 lowest p-values, so they are most likely to be related to QA.
