---
title: "Lab Assignment 3"
author: "Si Chen"
date: "11/28/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("~/Desktop/Everything Starts With Data/Lab Assignment 3")
library(quantreg)
library(e1071)
library(boot)
```

#Problem 1

##a)
The purpose of MCMC is to sample points from distribution $p(\cdot)$ that is difficult to sample from directly.

##b)
Metropolis Algorithm starts with an initial value $\theta_0$ and $q(\cdot|\cdot)$ need to be symmetric.


Metropolis Hastings Algorithm generalizes from the Metropolis Algorithm and $q(\cdot|\cdot)$ does not to have symmetric.

##c)
The purpose of Ridge Regression is to minimize SSE subject to $\lambda\sum\beta_j^2\leq s$


The purpose of Lasso Regression is to minimize SSE subject to $\lambda\sum|\beta_j|\leq s$


##d)
IIA is the ratio of the probabilities of choosing two alternatives is independent of the presence or attributes of any other alternative. 

#Problem 2

```{r}
gas = read.csv("gas_mileage.csv")
```

##a)
```{r}
qrfit1 = rq(Mpg ~ ., tau = seq(0.05, 0.95, by=0.05), data = gas)
sumqr = summary(qrfit1)
sumqr
```

##b)
```{r}
plot(qrfit1, mfrow =  c(2,2))
```

##c)
Length: Before 0.55th, with one unit increase th length, there will be on average 0.18 increase in mpg. From about 0.55th to 0.7th, the length has a drastic positive impact on mpg. After that the length has lesser positive impact on mpg. After 0.8th quantile the length has almost no influence on mpg.

Weight: Before 0.6th quantile, onw unit increase in weight will lead to about 0.18 increase in mpg. At 0.6th quantile, 0.1 unit increase in weight will lead to about 0.25 increase in mpg. After 0.8th quantile, weight has no influence on quantile.

comp_ratio: for most part, with the increase in comp_ratio, there will be a lesser negative impact in mpg But for comp_ratio at 0.6th quantile or after 0.8th quantile, it has a positive effect on mpg.


##d)
```{r}
median = rq(Mpg ~ ., tau = .5, data = gas)
summary(median, se = "boot")
```


#Problem 3

```{r}
car = read.csv("car.csv")
```

##a)
```{r}
carsvm = svm(factor(y) ~ ., data = car)
summary(carsvm)
```

##b)
```{r}
plot(carsvm, data = car, income ~ car_age)
```

##c)
```{r}
predict(carsvm, newdata = data.frame(income = 50, car_age = 5))
```

This family will purchase a new car.