---
title: "Lab Assignment 3"
author: "Si Chen"
date: "11/28/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("~/Desktop/Everything Starts With Data/Lab Assignment 3")
library(quantreg)
library(e1071)
library(boot)
```

#Problem 1

##a)
The purpose of MCMC is to sample points from distribution $p(\cdot)$ that is difficult to sample from directly.

##b)
Metropolis Algorithm starts with an initial value $\theta_0$ and $q(\cdot|\cdot)$ need to be symmetric.


Metropolis Hastings Algorithm generalizes from the Metropolis Algorithm and $q(\cdot|\cdot)$ does not to have symmetric.

##c)
The purpose of Ridge Regression is to minimize SSE subject to $\lambda\sum\beta_j^2\leq s$


The purpose of Lasso Regression is to minimize SSE subject to $\lambda\sum|\beta_j|\leq s$


##d)
IIA is the ratio of the probabilities of choosing two alternatives is independent of the presence or attributes of any other alternative. 

#Problem 2

```{r}
gas = read.csv("gas_mileage.csv")
```

##a)
```{r}
qrfit1 = rq(Mpg ~ ., tau = seq(0.05, 0.95, by=0.05), data = gas)
sumqr = summary(qrfit1)
sumqr
```

##b)
```{r}
plot(qrfit1, mfrow =  c(2,2))
```

##c)
Length: Before 0.55th, basically length has no influence on mpg. From about 0.55th to 0.7th, the length has a drastic positive impact on mpg. After that the length has negative impact on mpg.

Weight: before 0.5th, the mpg increases with weight increases. From 0.6th - 0.8th, the mpg decreases with weight increases. After 0.8th, the mpg increases with weight increases with a high degree.

comp_ratio: for most part, with the increase in comp_ratio, there will be a decrease in mpg.


##d)
```{r}
median = rq(Mpg ~ ., tau = .5, data = gas)
summary(median, se = "boot")
```


#Problem 3

```{r}
car = read.csv("car.csv")
```

##a)
```{r}
carsvm = svm(factor(y) ~ ., data = car)
summary(carsvm)
```

##b)
```{r}
plot(carsvm, data = car, income ~ car_age)
```

##c)
```{r}
predict(carsvm, newdata = data.frame(income = 50, car_age = 5))
```

This family will purchase a new car.